---
title: "Scraping_Airline_Data_Outline"
author: "Augustus Ge"
date: "November 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# We are hoping to help Brown University students who are looking to go on a winter vacation but cannot decide where to go. This will scrape flight options data to 10 popular vacation destinations and allow the user to view all relevant options with variables destination, price, duration, stops, rating, arline, airline company reviews (Tripadvisor), departure time, and arrival time.

# Initial query for flight 

```{r}
library(rvest)
library(httr)
session <- html_session("https://www.expedia.com/")
query1 <- "Boston, MA (BOS-All Airports)"
query2 <- "New York, NY (JFK-John F. Kennedy Intl.)"
query3 <- "12/12/2018"
form <- html_form(session)[[1]]
filled_form <- set_values(form, query1, query2)

session1 <- submit_form(session, filled_form)
```

```{r}

query = "data science"
loc = "Providence"
session <- html_session("https://www.indeed.com/jobs")
form <- html_form(session)[[1]]
filled_form <- set_values(form, q = query, l = loc)

session1 <- submit_form(session, filled_form)

```


```{r}
library(xml2)
library(rvest)
url <- "https://www.indeed.com/jobs?q=data+science&l=Providence%2C+RI"
webpage <- read_html(url)
# data <- dataframe(webpage)
# print(webpage)
html_nodes(html_attr(css = ))
```

```{r}

library(xml2)
library(rvest)

url_nyc <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ANew+York%2C+NY+%28JFK-John+F.+Kennedy+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY&fareCalendarPrice=1819"
webpage_nyc <- read_html(url_nyc)

url_tyo <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ATokyo%2C+Japan+%28HND-Haneda%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_tyo <- read_html(url_tyo)

url_mex <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3AMexico+City%2C+Distrito+Federal%2C+Mexico+%28MEX-Mexico+City+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_mex <- read_html(url_mex)

url_nas <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ANassau%2C+Bahamas+%28NAS-Nassau+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_nas <- read_html(url_nas)

url_bei <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ABeijing%2C+China+%28PEK-Capital+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_bei <- read_html(url_bei)

url_par <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3AParis%2C+France+%28CDG-Roissy-Charles+de+Gaulle%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_par <- read_html(url_par)

url_lon <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ALondon%2C+England%2C+UK+%28LHR-Heathrow%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_lon <- read_html(url_lon)

url_bcn <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ABarcelona%2C+Spain+%28BCN-Barcelona+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_bcn <- read_html(url_bcn)

url_lax <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3ALos+Angeles%2C+CA+%28LAX-Los+Angeles+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_lax <- read_html(url_lax)

url_hkg <- "https://www.expedia.com/Flights-Search?flight-type=on&starDate=12%2F21%2F2018&mode=search&trip=oneway&leg1=from%3ABoston%2C+MA+%28BOS-Logan+Intl.%29%2Cto%3AHong+Kong%2C+Hong+Kong+SAR+%28HKG-Hong+Kong+Intl.%29%2Cdeparture%3A12%2F21%2F2018TANYT&passengers=children%3A0%2Cadults%3A1%2Cseniors%3A0%2Cinfantinlap%3AY"
webpage_hkg <- read_html(url_hkg)

```

```{r}
# Now our goal is to use html_nodes and html_attr among others to parse the desired information: Destination, Price, Duration, Stops, Rating, Airline, Departure Time, Arrival Time

webpage_vecs <- c(webpage_nyc, webpage_tyo, webpage_mex, webpage_nas, webpage_bei, webpage_par, webpage_lon, webpage_bcn, webpage_lax, webpage_hkg)

destinations <- vector()
price <- vector()
duration <- vector()
stops <- vector()
rating <- vector()
airline <- vector()
dep_time <- vector()
arr_time <- vector()


# for(i in seq_along(webpage_vecs)){
#   # Destination
#   webpage_vecs[i] %>%
#     html_attr(html_nodes(css = "#flight-module-v5-450455ac4aac6daf64d618b4db0fdc1e-0-1\7e 2\2e S\7e AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\7e AQpDCiAI1JYBEgI4MhjBkwEgyJwBKNzPnwEwh9SfAThZQABYAQofCNSWARICNzAYyJwBIMcyKOTYnwEwvN2fAThZQAFYARIKCAEQARgBKgJUSxgBIgQIARABKAIoAygEMAI > div.grid-container.standard-padding > div.uitk-grid.all-grid-fallback-alt > div.uitk-col.all-col-fill.custom-short-r-margin > div > div > div > div.uitk-col.tablet-col-1-3.desktop-col-1-3.custom-col-r-margin.min-width-large-screens-only > div.secondary-content.route-happy-superlative.display-larger-screens-only > a"))
#   # Price
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Duration
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Stops
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Rating
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Airline
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Departure Time
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
#   # Arrival Time
#   webpage_vecs[i] %>%
#     html_attr(html_nodes())
# }

# Still trying to get the scraping to work
    html_text(html_nodes(webpage_nyc, css = "#flight-module-v5-4e51ba3f4dd33d3edd4584bb4c029f6b-6-1\~2\.S\~AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\~AQpnCiIIxZYBEgQ2MDMzGMGTASDEjQEosMifATCLyZ8BOE1AAFgBCiAIxZYBEgMyMjQYxI0BIOMNKJbKnwEwhNCfAThNQAFYAQofCMWWARIDMzg2GOMNIMcyKI7VnwEwqNifAThNQAFYARIKCAEQARgBKgJFSxgBIgQIARABKAIoAygEMAI .standard-padding , #flight-module-v5-4e51ba3f4dd33d3edd4584bb4c029f6b-5-1\~2\.S\~AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\~AQpnCiIIxZYBEgQ2MDMzGMGTASDEjQEosMifATCLyZ8BOE1AAFgBCiAIxZYBEgMyMjQYxI0BIOMNKJbKnwEwhNCfAThNQAFYAQofCMWWARIDMzgwGOMNIMcyKOPQnwEwkdSfAThNQAFYARIKCAEQARgBKgJFSxgBIgQIARABKAIoAygEMAI .standard-padding , #flight-module-v5-4e51ba3f4dd33d3edd4584bb4c029f6b-4-1\~2\.S\~AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\~AQppCiII1YIBEgQyMDc3GMGTASDEjQEosMifATCHyZ8BOFVAAFgBCiAI1YIBEgI3ORjEjQEgrZwBKJvKnwEw6NCfAThVQAFYAQohCNWCARIENzk4ORitnAEgxzIotdKfATDw1J8BOFVAAVgBEgoIARABGAEqAlVBGAEiBAgBEAEoAigDKAQwAg .standard-padding , #flight-module-v5-4e51ba3f4dd33d3edd4584bb4c029f6b-2-1\~2\.S\~AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\~AQppCiII1YIBEgQyMTY1GMGTASDEjQEo7sifATDGyZ8BOFVAAFgBCiAI1YIBEgI3ORjEjQEgrZwBKJvKnwEw6NCfAThVQAFYAQohCNWCARIENzk4ORitnAEgxzIotdKfATDw1J8BOFVAAVgBEgoIARABGAEqAlVBGAEiBAgBEAEoAigDKAQwAg .standard-padding , #flight-module-v5-4e51ba3f4dd33d3edd4584bb4c029f6b-0-1\~2\.S\~AQoCCAESBwjUBBABGAEgASAHIAkgDSAMKAJYAQ\~AQpDCiAI1JYBEgI4MhjBkwEgyJwBKNzPnwEwh9SfAThZQABYAQofCNSWARICNzAYyJwBIMcyKOTYnwEwvN2fAThZQAFYARIKCAEQARgBKgJUSxgBIgQIARABKAIoAygEMAI .standard-padding"))


```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
